---
title: "Covid cases"
output:
  html_document:
    df_print: paged
  word_document: default
---

## Introduction

Our objective is to see how to create a document using R.

The document will combine:
- text
- code
- R output

The document will be in html, so we can use both as a text document and for presentation. 

Specialized formats are also available, but this is a flexible method. 

##

Types of commonly used files

- .csv for data
- .R for R script, writing commands that can be clicked
- .Rmd (R notebook) (will produce html)
- .html (can be viewed in a web browser like Google chrome)

## Data

```{r}
owid_ies <- read.csv("~/Documents/R/math_R/owid_ies.csv")
```


Data is from the Our World in Data website, publicly available and easily *downloadable*. 

We look at the structure of the data with str(). 

```{r}
str(owid_ies)
```

We change location variable to a factor. 

```{r}
owid_ies$location <- factor(owid_ies$location)
str(owid_ies$location)
```

We load packages. 
```{r}
library(ggplot2) # for plotting
library(dplyr) # for working with data
library(scales) # for working with scales
library(lubridate) # for dates
library(ggthemes) # for themes of graph
```

We work with dates.

```{r}
owid_ies$date <- ymd(owid_ies$date)
datebreaks <- seq(as.Date("2020-01-01"),
                  as.Date("2021-07-01"),
                  by = "6 month")
```

We plot the figure.

```{r fig.height = 4, fig.width = 4}


gg3 <- 
  ggplot(owid_ies, aes(x = date,
            y = new_cases_smoothed_per_million,
            group = location)) +
  geom_line() + 
  facet_wrap(~location, scales = "free_y",
             ncol = 2) +
  scale_x_date(breaks = datebreaks,
               labels = date_format("%Y %b")) +
    theme(axis.text.x = element_text(
      angle = 30)) +
  xlab("") +
  ggtitle("COVID-19 cases") +
  theme_fivethirtyeight(base_size = 9)
library(plotly)
ggplotly(gg3)
```

## Discussion

Different countries experienced COVID-19 in waves.